Exploring Local Explanations of Non-linear Models Using Animated Linear Projections

### 2022-01-11 _paper.rmd
looked at the regression case studies but they need more work

With figure \@ref(fig:casefifa), we will test the premise of the local explanation. While `offense` and `reaction` skills both crutial to the explaintion of a star offensive player. We increase the contribution of denfensive skills and Messi is no longer separated from the group while van Dijk and other defensive players are better explained in this case.

@@

>>>>

With figure \@ref(fig:casefifa), we will test the premise of the local explanation. While `offense` and `reaction` skills both crutial to the explanation of a star offensive player. We increase the contribution of denfensive skills and Messi is no longer separated from the group while van Dijk and other defensive players are better explained in this case.

XXX think about the projection as a what if. So for Messi, if his new stats were .... (those shown in second projection) then is salary would be predicted to be halved.

@@

XXX Observation 170, big residual; maybe look at obs 33

### 2022-01-11 _paper.tex
looked at the regression case studies but they need more work

With figure \ref{fig:casefifa}, we will test the premise of the local explanation. While \texttt{offense} and \texttt{reaction} skills both crutial to the explaintion of a star offensive player. We increase the contribution of denfensive skills and Messi is no longer separated from the group while van Dijk and other defensive players are better explained in this case.

>>>>

With figure \ref{fig:casefifa}, we will test the premise of the local explanation. While \texttt{offense} and \texttt{reaction} skills both crutial to the explanation of a star offensive player. We increase the contribution of denfensive skills and Messi is no longer separated from the group while van Dijk and other defensive players are better explained in this case.

XXX think about the projection as a what if. So for Messi, if his new stats were \ldots. (those shown in second projection) then is salary would be predicted to be halved.
